Size Convergence of the E$\times$B \\ Staircase Pattern in Flux Tube \\ Simulations of Ion Temperature \\ Gradient-Driven Turbulence

### 2023-06-29 presentation/presentation.tex
#39: Correction presentation

	\begin{frame}
		\frametitle{Ion Temperature Gradient (ITG)-driven Instability}
		\begin{center}
			\onslide<2->\input{../pictures/Theory/ITG-Turbulence_Presentation.tex}
		\end{center}
	\end{frame}

@@

		\begin{center}
			\begin{itemize}
				\item <2-> Simulation setup orientates on Paper from Arthur Peeters in the year 2016
				\item <2-> Non-linear flux tube version of Gyrokinetic Workshop (GKW) 
				\item <3-> Circular concentric flux surfaces 
				\item <4-> Standard resolution with 6th order (S6) 
				\item <5-> Cyclone Base Case (CBC) parameters $\rlt = 6.0$ 
				\item <6-> Turbulence level is quantified by the turbulent heat conduction coefficient $\chi$
				%\item <7-> Quantities $\rhoth$, $R$, $T$, $\vth$ and $m$ are referenced quantities
				\item <7-> Standard box size $(L_\xcoord,~L_\ycoord) = (76.3,~89.8)\,\rhoth$
			\end{itemize}
			\onslide<4->{
			\bigskip
			\begin{tabular}{l | ccccc | ccccc | c | cc}
				& $N_\mathrm{m}$ & $N_x$ & $N_\mathrm{s}$ & $N_{\nu_\parallel}$ & $N_\mu$ & $D$ & $\nu_\mathrm{d}$           & $D_{\nu_\parallel}$ & $D_x$ & $D_y$ & Order & $k_y\rho$ & $k_x\rho$ \\
				\hline
				S6   & 21    & 83    & 16    & 64                  & 9       & 1   & $|\nu_\parallel|$ & 0.2                 & 0.1   & 0.1   & 6     & 1.4       & 2.1       \\
			\end{tabular}}
		\end{center}
	\end{frame}

@@

	\begin{frame}
		\frametitle{Variation of Computational Resolution}
		\pause
		\textbf{Goals:}
		\begin{itemize}
			\item Estimate the minimal resolution without numerical dissipation
			\item Reduce \textbf{calculation time} and \textbf{costs} of the simulation
		\end{itemize}
		\pause
		\textbf{Criteria:}
		\begin{enumerate}
			\item[\textbf{(1)}] Subdued turbulence after \textbf{short} time periods
			\item[\textbf{(2)}] Stability for \textbf{long} time periods 
		\end{enumerate}
		\pause
		\textbf{Verification:}
		\begin{enumerate}
			\item Reduce only one number of grid points and look if criterias \textbf{(1), (2)} are satisfied
			\item Reduce to known the minimum number of grid points to verify result in general.
		\end{enumerate}
	\end{frame}

@@

				$\Rightarrow$ Mesoscale pattern size of: \\[0.3cm]
				$\boxed{\sim 57 - 76\,\rhoth}$ \bigskip

@@

		\begin{minipage}{0.4\paperwidth}\raggedleft
			\begin{itemize}
				\item <2-> Parallel velocity $\Nvpar$ could be reduced from 64 to 48, which halfed the time until suppression of turbulence
				\item <3-> Restart Script with \texttt{python} led to further convenience during the task of performing simulations
				\item <4-> Mesoscale pattern size of $\sim 57 - 76\,\rhoth$ is found to be intrinsic to ITG-driven turbulence for Cyclone Base Case parameters
				\item <5-> Finite heat flux threshold is located at $\rlt|_\mathrm{finite} = 6.3 \pm 0.1$
			\end{itemize}
		\end{minipage}
		\begin{minipage}{0.4\paperwidth}
			\onslide<4-> \includegraphics[width = 0.5\paperwidth]{Comparison/Boxsize/S6_rlt6.0_boxsize1-2-3-4x1-1.5-2-2.5-3-5_Ns16_Nvpar48_Nmu9_wexb_comparison_thesis.pdf}
		\end{minipage}
	\end{frame}

>>>>

	\begin{frame}
		\frametitle{Ion Temperature Gradient (ITG)-driven Instability}
		\begin{center}
			\only<1>{\includegraphics[width=0.6\paperwidth]{Theory/Tokamak-Torus.pdf}}

			\onslide<2->\input{../pictures/Theory/ITG-Turbulence_Presentation.tex}
		\end{center}
	\end{frame}

@@

		\begin{center}
			\begin{itemize}
				\item <2-> Simulation setup based on Peeters et al. 2016
				\item <3-> Non-linear flux tube version of Gyrokinetic Workshop (GKW) with field aligned Hamada coordinates
				\item <4-> Standard resolution with 6th order (S6) 
				\item <5-> Cyclone Base Case (CBC) parameters with circular concentric flux surfaces and $\rlt = 6.0$ 
				\item <6-> Turbulence level is quantified by the turbulent heat conduction coefficient $\chi$
				%\item <7-> Quantities $\rhoth$, $R$, $T$, $\vth$ and $m$ are referenced quantities
				\item <7-> Standard box size $(L_\xcoord,~L_\ycoord) = (76.3,~89.8)\,\rhoth$
			\end{itemize}
			\onslide<4->{
			\bigskip
			\begin{tabular}{l | ccccc | ccccc | c | cc}
				& $N_\mathrm{m}$ & $N_x$ & $N_\mathrm{s}$ & $N_{\nu_\parallel}$ & $N_\mu$ & $D$ & $\nu_\mathrm{d}$           & $D_{\nu_\parallel}$ & $D_x$ & $D_y$ & Order & $k_y\rho$ & $k_x\rho$ \\
				\hline
				S6   & 21    & 83    & 16    & 64                  & 9       & 1   & $|\nu_\parallel|$ & 0.2                 & 0.1   & 0.1   & 6     & 1.4       & 2.1       \\
			\end{tabular}}
		\end{center}
	\end{frame}

@@

	\begin{frame}
		\frametitle{Variation of Computational Resolution}
		\pause
		\textbf{Goals:}
		\begin{itemize}
			\item Estimate the minimal resolution without numerical dissipation
			\item Reduce \textbf{calculation time} and \textbf{costs} of the simulation
		\end{itemize}
		\pause
		\textbf{Criteria:}
		\begin{enumerate}
			\item[\textbf{(1)}] Subdued turbulence after \textbf{short} time periods
			\item[\textbf{(2)}] Stability for \textbf{long} time periods 
		\end{enumerate}
		\pause
		\textbf{Verification:}
		\begin{enumerate}
			\item Reduce only one number of grid points and look if criteria \textbf{(1), (2)} are satisfied,
			\item Reduce to the known minimum number of grid points to verify result in general.
		\end{enumerate}
	\end{frame}

@@

				$\Rightarrow$ Mesoscale pattern size of: \\[0.3cm]
				$\boxed{\sim (57 - 76)\,\rhoth}$ \bigskip

@@

		\begin{minipage}{0.4\paperwidth}\raggedleft
			\begin{itemize}
				\item <2-> Restart Script with \texttt{python} led to further convenience during the task of performing simulations
				\item <3-> Finite heat flux threshold is located at $\rlt|_\mathrm{finite} = 6.3 \pm 0.1$
				\item <4-> Parallel velocity $\Nvpar$ could be reduced from 64 to 48, which halfed the time until suppression of turbulence
				\item <5-> Mesoscale pattern size of $\sim (57 - 76)\,\rhoth$ is found to be intrinsic to ITG-driven turbulence for Cyclone Base Case parameters
			\end{itemize}
		\end{minipage}
		\begin{minipage}{0.4\paperwidth}
			\onslide<5-> \includegraphics[width = 0.5\paperwidth]{Comparison/Boxsize/S6_rlt6.0_boxsize1-2-3-4x1-1.5-2-2.5-3-5_Ns16_Nvpar48_Nmu9_wexb_comparison_thesis.pdf}
		\end{minipage}
	\end{frame}
